Supporting Information

### 2017-02-09 code/rmarkdown/supporting-information.Rmd
update si

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifer, and using a boundary length modifier of `r max(benchmark.params.LST[[MODE]]$blm`. To assess variation in solve times, we generated and solved `r benchmark.params.LST[[MODE]]$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) and a an Intel(R) Xeon(R) CPU E5-2630 (version 3; 2.40 GHz). To provide comparable estimates for the typical user, problems were solved using `r as.english(general.params.LST[[MODE]]$threads)` threads.

>>>>

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifer, and using a boundary length modifier of `r max(benchmark.params.LST[[MODE]]$blm)`. To assess variation in solve times, we generated and solved `r benchmark.params.LST[[MODE]]$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) and a an Intel(R) Xeon(R) CPU E5-2630 (version 3; 2.40 GHz). To provide comparable estimates for the typical user, problems were solved using `r as.english(general.params.LST[[MODE]]$threads)` threads.
